### 2021-09-09 tex/ms.tex
Maths
Rewrite squashing function

Let the squashing function be
\begin{align}
S(x)
    &= \asin(x) \\
    &= \log\left(x + \sqrt{x^2 + 1}\right).    
\end{align}

There is a trig identity for addition:
\begin{align}
\asin u + \asin v &= \asin\left(u\sqrt{1+v^2} + v\sqrt{1+u^2}\right).
\end{align}
If we associate $u\sqrt{1+v^2}$ with the existing trending score
and $v\sqrt{1+u^2}$ with the spike mass, then the left hand side may be used
to compute the updated trending score, once we solve for $u$ and $v$.

Let $x$ be the old trending score and $m$ be the spike mass before scaling.
Then we have
\begin{align}
x &= u\sqrt{1+v^2} \\
m\exp(t/L) &= v\sqrt{1+u^2}.
\end{align}
We must now solve for $u$ and $v$ in terms of $x$ and $m$.

>>>>

Let the squashing function be
\begin{align}
S(x) &=
    \left\{
        \begin{array}{lr}
            \log (1 + x), & \textnormal{if } x \geq 0, \\
            -\log(1 - x), & \textnormal{otherwise}.
        \end{array}
    \right.
\end{align}
Operations on the squashed grade can be defined in terms of logsumexp
and logdiffexp, to avoid overflow.
